---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get-started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(htmltools)
```

```{r setup}
library(mobileCharts)
```

## Basics

It looks an aweful lot like [ggplot2](https://ggplot2.tidyverse.org/). Initialise the chart with `mobile` then pipe (`%>%`) geometries and other options, evey function starts with `mobile`.

```{r}
mobile(cars, aes(speed, dist)) %>% 
  mobile_point()
```

## Tooltips

Since this package generates charts for the mobile tooltips work on click not on hover.

```{r}
mobile(cars, aes(speed, dist)) %>% 
  mobile_point() %>% 
  mobile_tooltip(snap = TRUE)
```

## Pie

mobileCharts is still in early development and some things may look odd, i.e.: how one builds a pie chart. A pie chart is, to mobileCharts, a stacked bar on a polar axis.

```{r}
df <- data.frame(
 label = c("banana", "apple", "cake"),
 value = c(50, 30, 20),
 x = "1" # phoney variable
)

mobile(df, aes(x, value, color = label, adjust = stack)) %>% 
 mobile_bar() %>% 
 mobile_coord("polar", transposed = TRUE) %>% 
 mobile_hide_axis()
```

## Flip Coordinates

You can also use `mobile_coord` to flip the coordinates.

```{r}
df <- data.frame(x = LETTERS[1:3], y = c(10, 20, 15))
mobile(df, aes(x, y)) %>% 
  mobile_bar() %>% 
  mobile_coord("rect", transposed = TRUE)
```

## Legend

You can manipulate the legend with `mobile_legend`.

```{r}
mobile(iris, aes(Petal.Length, Petal.Width, color = Species)) %>% 
  mobile_point() %>% 
  mobile_legend(position = "right")
```

## Scale

You can adjust the scaling with `mobile_scale`.

```{r}
mobile(cars, aes(speed, dist, size = dist)) %>% 
  mobile_point() %>% 
  mobile_scale_y(max = 150, tickCount = 50)
```

## Heatmap

You can use `mobile_polygon` to create a heatmap.

```{r}
df <- expand.grid(x = LETTERS, y = LETTERS)
df$z <- runif(nrow(df))
mobile(df, aes(x, y, color = z)) %>% 
  mobile_polygon()
```

## Combine

You are not limited to a single geom of course.

```{r}
mobile(mtcars, aes(qsec, wt)) %>% 
  mobile_area() %>% 
  mobile_line() %>% 
  mobile_point(aes(y = mpg, color = "red"))
```

## Interactions

The functions `mobile_interaction` and `mobile_scroll` will let you customise interactions with the charts. The latter function simply adds a scrollbar.

```{r}
df <- data.frame(
  x = 1:20,
  y = runif(20, 1, 10)
)

# pan limits
lmt <- list(x = list(min = -20, max = 20))

mobile(df, aes(x, y)) %>% 
  mobile_bar() %>% 
  mobile_interaction("bar-select") %>% # highlight on select
  mobile_interaction("pan", limitRange = lmt) %>% 
  mobile_scroll(mode = "x", xStyle = list(offsetY = -5))
```

## Themes

You can define your own theme with `mobile_theme`.

```{r}
mob <- mobile(iris, aes(Petal.Length, Petal.Width, color = Species)) %>% 
  mobile_point() 

# get plasma colors
colors <- viridis::plasma(4)

mob %>% 
  mobile_theme(colors)

# ggplot2 emulation
mob %>% 
  mobile_ggplot_theme(n = 4)

mob %>% 
  mobile_theme(colors = c("#ffffff"), background_color="#000000")
```
